---
title: "Data Visualization with JavaScript powered packages"
author: "Zanin Pavel"
date: "March 10, 2016"
output: html_document
---

# Introduction

[Link to project on GitHUB](https://github.com/Filareth2015/Solutions-collection)

HTML widgets work just like R plots except they produce interactive web visualizations. A line or two of R code is all it takes to produce a D3 graphic or Leaflet map.   

All examples were took from [htmlwidgets](http://www.htmlwidgets.org/showcase_leaflet.html) 

Examples list:     
1. Geo-spatial mapping    
2. Time series charting   
3. Interactive graphics    
4. Highcharts   
5. Graph visualization   
6. Interactive heatmap    
7. Tabular data dysplay    
8. 3D scatterplot and 3D globe    
9. Renders WebGL scenes    
10. Diagrams and flowcharts    
11. Scatterplots, line charts, and histograms    

## Geo-spatial mapping

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=30.316163, lat=59.939029, popup="Saint Petersburg, Palace square")
m  # Print the map
```



## Time series charting

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```


## Interactive graphics

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
d <- diamonds[sample(nrow(diamonds), 500), ]
plot_ly(d, x = carat, y = price, text = paste("Clarity: ", clarity),
        mode = "markers", color = carat, size = carat)
```


## Highcharts

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(magrittr)
library(highcharter)
highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_serie_scatter(mtcars$wt, mtcars$mpg,
                       mtcars$drat, mtcars$hp)
```

## Graph visualization

### vis.js

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(visNetwork)
nodes <- data.frame(id = 1:6, title = paste("node", 1:6), 
                    shape = c("dot", "square"),
                    size = 10:15, color = c("blue", "red"))
edges <- data.frame(from = 1:5, to = c(5, 4, 6, 3, 3))
visNetwork(nodes, edges) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)
```

### D3

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(networkD3)
data(MisLinks, MisNodes)
forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.4)
```

## Interactive heatmap

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(d3heatmap)
d3heatmap(mtcars, scale="column", colors="Blues")
```

## Tabular data dysplay

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(DT)
datatable(iris, options = list(pageLength = 5))
```

## 3D scatterplot and 3D globe

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(threejs)
z <- seq(-10, 10, 0.01)
x <- cos(z)
y <- sin(z)
scatterplot3js(x,y,z, color=rainbow(length(z)))
```

## Renders WebGL scenes

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(rgl)
library(rglwidget)
library(htmltools)

theta <- seq(0, 6*pi, len=100)
xyz <- cbind(sin(theta), cos(theta), theta)
lineid <- plot3d(xyz, type="l", alpha = 1:0, 
                 lwd = 5, col = "blue")["data"]

browsable(tagList(
  rglwidget(elementId = "example", width = 500, height = 400,
            controllers = "player"),
  playwidget("example", 
             ageControl(births = theta, ages = c(0, 0, 1),
                        objids = lineid, alpha = c(0, 1, 0)),
                        start = 1, stop = 6*pi, step = 0.1, 
                        rate = 6,elementId = "player")
))
```


## Diagrams and flowcharts

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(DiagrammeR)
grViz("
  digraph {
    layout = twopi
    node [shape = circle]
    A -> {B C D} 
  }")
```


## Scatterplots, line charts, and histograms

```{r, collapse = TRUE, warning=FALSE, message = FALSE, echo=TRUE, results='markup'}
library(metricsgraphics)
mjs_plot(mtcars, x=wt, y=mpg) %>%
  mjs_point(color_accessor=carb, size_accessor=carb) %>%
  mjs_labs(x="Weight of Car", y="Miles per Gallon")
```
