---
title: "Does drinking beer make you more attractive to mosquitos?"
author: "Zanin Pavel"
date: "March 12, 2016"
output: html_document
---

[Link on GitHUB](https://github.com/Filareth2015/Solutions-collection/tree/master/Simple%20statistic)

## Introduction

Here I'm going to answer on next question: Does drinking beer make you more attractive to mosquitos?

Ideas and data were took from examples in [link](https://www.youtube.com/watch?t=672&v=5Dnw46eC-0o)

List of activities:    
* Expolratory data analysis    
* Test of hypotheses     
* Permutation test    

## Data processing

### Expolratory data analysis

Reading the data
```{r, collapse = TRUE, warning=FALSE, message = FALSE}

library(ggplot2) 
library(dplyr)

set.seed(12345)

dataset <- read.csv("dataset.csv", head=TRUE) 

```

Look at the data quickly with summary() and head().
```{r, collapse = TRUE, warning=FALSE, message = FALSE}
summary(dataset)
head(dataset)
```
So, we have 25 records for subjects, who drunk beer and 18 for who drunk water.

Let's calculate mean for each group
```{r, collapse = TRUE, warning=FALSE, message = FALSE}
means <- dataset %>%
  group_by(Type) %>%
  summarise(mean(Count))
means
```

Difference between beer and water means:
```{r, echo=FALSE, collapse = TRUE, warning=FALSE, message = FALSE}
water <- filter(dataset, Type =="Water") 

beer <- filter(dataset, Type =="Beer") 

observedStat <- mean(beer$Count) - mean(water$Count)
observedStat
```

For the next step let's make exploratory plot's for this data:
```{r, collapse = TRUE, warning=FALSE, message = FALSE}
g <- ggplot(dataset, aes(dataset$Type, dataset$Count, fill = Type, ymin = 10, ymax = 30)) +
  geom_point(colour = "red", size = 4) + 
  geom_boxplot(aes(fill = dataset$Type)) +
  labs(title="The number of bites by mosquitoes", 
    x="Subjects",
    y="Count")
g
```

**Infer:** Difference between means (`r round(observedStat, 2)`). Is it a sufficient evidence to claim that drinking beer makes you more attractive for moquitos?  

### Hypotheses test 

Let's test null hypithesis: means for each types are equal.

```{r, collapse = TRUE, warning=FALSE, message = FALSE}
t.test(Count ~ Type, data = dataset)$p.value

t.test(Count ~ Type, data = dataset)$conf.int
```

**Infer:**  P-value less than significance level (0.05), so we reject null hypothesis. Means for each types are different. 


### Permutation test

Let's test null hypothesis that the labels are irrelevant (exchangeable). This is a handy way to create a null distribution for our test statistic by simply permuting the labels over and over and seeing how extreme our data are with respect to this permuted distribution. The procedure would be as follows:      
1. consider a data from with count and type,         
2. permute the type (group) labels,     
3. recalculate the statistic (such as the difference in means),     
4. calculate the percentage of simulations where the simulated statistic was more extreme (toward the alternative) than the observed.  

```{r, collapse = TRUE, warning=FALSE, message = FALSE}
group <- as.character(dataset$Type)

testStat <- function(w, g) {mean(w[g == "Beer"]) - mean(w[g == "Water"])}

observedStat <- testStat(dataset$Count, group)
observedStat

permutations <- sapply(1 : 50000, function(i) testStat(dataset$Count, sample(group)))
round(mean(permutations > observedStat, 3))

hist(permutations, col = "#62829C", breaks = 50000)
abline(v = observedStat, lwd=3, col = "red")
abline(v = 0, lwd=2, col = "blue", se = FALSE)
```

**Infer:**  We reject null hypothesis. Data for both types have differences. 

## Conclusions
Drinking beer makes you more attractive for mosquitos.
